The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-05 analysis/paper/paper.qmd

```{r topic-model-lda}

@@

# TODO can this be generalised to more than two topics?
beta_spread <- emu_theses_topics |> 
  mutate(topic = paste0("topic", topic)) |> 
  spread(topic, beta) |> 
  filter(topic1 > 0.001, topic2 > .001) |> 
  mutate(log_ratio = log2(topic2/topic1))

>>>>

```{r topic-model-lda}
emu_theses_topics <- get_topics(emu_theses_words)

emu_theses_topics_terms <- tidy(emu_theses_topics, matrix = "beta")
emu_theses_topics_documents <- tidy(emu_theses_topics, matrix = "gamma")

@@

# TODO can this be generalised to more than two topics?
# beta_spread <- emu_theses_topics_terms |> 
beta_spread <- emu_theses_topics |> 
  mutate(topic = paste0("topic", topic)) |> 
  spread(topic, beta) |> 
  filter(topic1 > 0.001, topic2 > .001) |> 
  mutate(log_ratio = log2(topic2/topic1))
